---
title: "RUCOOL July 2025 Budget Report"
format: revealjs
editor: visual
---

```{r}
library(knitr)
library(tidyverse)
library(kableExtra)
library(dplyr)
library(gt)
library(lubridate)
library(readxl)

pb <- read_excel("Downloads/COOL 20250702 Projects Consolidated View By Task.xlsx")
pb = filter(pb, `Current Project Status Name` %in% "Active")
pb$`Sponsor End Date` = as.POSIXct(pb$`Sponsor End Date`, format = "%m/%d/%Y")
```

## Ended 6/30 but still listed as active
DEP glider getting NCE. 
New Cinar getting NCE  
MBON new money coming but might be new account?   

```{r}
n=c(1:8) 
kable(pb[n,], format.args = list(big.mark = ",")) %>% kable_styling(font_size = 12)
```

# Under 3 months 
to Oct. 2025

## MARACOOS

```{r}
n=c(9:15)
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```

`r x`% spent

Glider (Aug/Sept), Mike (Jan), Satellite (June - Steve will bring to zero), HFR (Nov or Feb), Modeling, Data to Model (Smith), DAC

```{r}
n=c(9:15)
difftime(strptime(pb$`Sponsor End Date`[n], format = "%Y-%m-%d"), + strptime("2025-07-08", format = "%Y-%m-%d"),units="days")

kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 10)
```

## NOAA Glider Training

```{r}
n=16
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```

`r x`% spent

No one charge to it until Mike says
```{r}
n=16
difftime(strptime(pb$`Sponsor End Date`[n], format = "%Y-%m-%d"), + strptime("2025-07-08", format = "%Y-%m-%d"),units="days")

kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15)
```

## Hurricane Supp.

```{r}
n=18
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```

`r x`% spent  

$70k coming for new account. Mike charging 20%, could add another glider person in Aug.  

```{r}
n=18
difftime(strptime(pb$`Sponsor End Date`[n], format = "%Y-%m-%d"), + strptime("2025-07-08", format = "%Y-%m-%d"),units="days")

kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15)
```

## UVI

```{r}
n=19
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```

`r x`% spent. 

Will there be more money? Brian and Jess can charge this out. 

```{r}
n=19
difftime(strptime(pb$`Sponsor End Date`[n], format = "%Y-%m-%d"), + strptime("2025-07-08", format = "%Y-%m-%d"),units="days")

kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15)
```

## Ramboll

```{r}
n=20
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```

`r x`% spent

Stopwork order. Daphne summer and then the remainder goes back.

```{r}
n=20
difftime(strptime(pb$`Sponsor End Date`[n], format = "%Y-%m-%d"), + strptime("2025-07-08", format = "%Y-%m-%d"),units="days")

kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15)
```

## BPU Wind

```{r}
n=21
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```

`r x`% spent

Fernando 60%, Mike 10%, Julia 100% until Aug. 31. Summer still needs to be posted. Will revisit end of July.

```{r}
n=21
difftime(strptime(pb$`Sponsor End Date`[n], format = "%Y-%m-%d"), + strptime("2025-07-08", format = "%Y-%m-%d"),units="days")

kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15)
```

## SOCCOM

```{r}
n=c(17,22)
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```

`r x`% spent

SOCCOM 2: Need to charge another month of Oscar, summer for Quentin, Mya, and Teemer. SOCCOM 3: Year 1 of 4

```{r}
n=c(17,22)
difftime(strptime(pb$`Sponsor End Date`[n], format = "%Y-%m-%d"), + strptime("2025-07-08", format = "%Y-%m-%d"),units="days")

kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15) 
```

## RIOS

```{r}
n=24
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```

`r x`% spent

```{r}
n=24
difftime(strptime(pb$`Sponsor End Date`[n], format = "%Y-%m-%d"), + strptime("2025-07-08", format = "%Y-%m-%d"),units="days")

kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15)
```

# Under 6 months 
to Jan. 2026

## SNJ-DEP Ecoglider Phase 1

```{r}
n=25
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```

`r x`% spent

100% Delphine, 65% Lori, 60% Jess, 70% Brian charging. Jake salary, fall salary and tuition for Sam, Ashley, and Izzy tuition, Lauren summer. Still more to spend (~$60-70k)

```{r}
n=25
difftime(strptime(pb$`Sponsor End Date`[n], format = "%Y-%m-%d"), + strptime("2025-07-08", format = "%Y-%m-%d"),units="days")

kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15)
```

## Cod 

User fees need to be taken out ($15k). Jasco still needs to send final invoice for SRW ~$33k (sent it for REV already). Steve split the Jasco invoices between REV and SRW, and should already be moved (Steve will check). 

```{r}
n=c(26,33)
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```

`r x`% spent

```{r}
n=c(26,33)
difftime(strptime(pb$`Sponsor End Date`[n], format = "%Y-%m-%d"), + strptime("2025-07-08", format = "%Y-%m-%d"),units="days")

kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15)
```

## SNJ-DEP RMI Ocean Observing

```{r}
n=27
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```

`r x`% spent

All for subcontracts (~$53k)

```{r}
n=27
difftime(strptime(pb$`Sponsor End Date`[n], format = "%Y-%m-%d"), + strptime("2025-07-08", format = "%Y-%m-%d"),units="days")

kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15)
```

## Seaforestation

```{r}
n=28
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```

`r x`% spent

Charge Aug. for Oscar (~45k), travel, Jess 40% salary, Joe glider camp. User fee still needs to be charged ($20k)

```{r}
n=28
difftime(strptime(pb$`Sponsor End Date`[n], format = "%Y-%m-%d"), + strptime("2025-07-08", format = "%Y-%m-%d"),units="days")

kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15)
```

## WAP UConn

```{r}
n=29
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```

`r x`% spent

Mostly students (Teemer, Myam Quintin) and people we send to Antarctica. Account was set up late

```{r}
n=29
difftime(strptime(pb$`Sponsor End Date`[n], format = "%Y-%m-%d"), + strptime("2025-07-08", format = "%Y-%m-%d"),units="days")

kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15)
```


