---
title: "Jan. Budget Review"
format: revealjs
editor: visual
---

```{r}
library(knitr)
library(tidyverse)
library(kableExtra)
library(dplyr)
library(gt)
library(lubridate)
library(readxl)

pb <- read_excel("~/Downloads/20260113 COOL Balances.xlsx", skip=3)
  #read_excel("~/Downloads/Balance Report 20250826 (1).xlsx", skip=3)
#pb = filter(pb, `Current Project Status Name` %in% "Active") 
pb$`Sponsor End Date` = as.POSIXct(pb$`Sponsor End Date`, format = "%m/%d/%Y")
pb = arrange(pb, `Sponsor End Date`)
pb = filter(pb, `Sponsor End Date` > "2026-01-01") %>%
  dplyr::select(-`Current Project Manager`,-`Current Project Status Name`)
pb = pb %>% rename(Cost = `Raw Cost`) #pb$Cost = pb$`Raw Cost` # names change in this file
            
difftime_func <- function(n){
    difftime(strptime(pb$`Sponsor End Date`[n], format = "%Y-%m-%d"), 
             + strptime("2026-01-15", format = "%Y-%m-%d"), 
             units="days")
  }
```

# 3 Months

April 2026

## WAP UConn (837205)

```{r}
n=1
x = format((pb$Cost[n]/pb$Budget[n])*100, digits = 2)
```

`r x`% spent

Year 1 of 4 years. Mostly students (Teemer, Mya, Quintin) and people we send to Antarctica.

```{r}
n=1
round(difftime_func(n))
kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15) %>%
      row_spec(row = 0, color = "navy", background = "lightcyan")
```

## MOCEAN (837207)

```{r}
n=3
x = format((pb$Cost[n]/pb$Budget[n])*100, digits = 2)
```

`r x`% spent.

Remaining goes to Sarah and Daphne

```{r}
n=3
round(difftime_func(n))
kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15) %>%
      row_spec(row = 0, color = "navy", background = "lightcyan")
```

## BOEMRE NYB Sands (832319)

```{r}
n=4
x = format((pb$Cost[n]/pb$Budget[n])*100, digits = 2)
```

`r x`% spent.

Motz asked for NCE. Mike Smith will be charged here (TBD maybe 40% starting Jan.),

```{r}
n=4
round(difftime_func(n))
kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15) %>%
      row_spec(row = 0, color = "navy", background = "lightcyan")
```

## ASOW Lidar at RUMFS (837206)

```{r}
n=5
x = format((pb$Cost[n]/pb$Budget[n])*100, digits = 2)
```

`r x`% spent.

RUMFS can't use it, Mike will spend it out.

```{r}
n=5
difftime_func(n)
kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15) %>%
      row_spec(row = 0, color = "navy", background = "lightcyan")
```

## Nantucket Shoals (837326)

```{r}
n=6
x = format((pb$Cost[n]/pb$Budget[n])*100, digits = 2)
```

`r x`% spent

```{r}
n=6
round(difftime_func(n))
kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15) %>%
      row_spec(row = 0, color = "navy", background = "lightcyan")
```

## 6 months

July 2026

## Moffet CAREER (829976)

```{r}
n=7
x = format((pb$Cost[n]/pb$Budget[n])*100, digits = 2)
```

`r x`% spent

```{r}
n=7
round(difftime_func(n))
kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15) %>%
      row_spec(row = 0, color = "navy", background = "lightcyan")
```

## 2024 NJDEP (838607)

```{r}
n=9
x = format((pb$Cost[n]/pb$Budget[n])*100, digits = 2)
```

`r x`% spent

Spending it on the 2025 deployment. Steve did user fee. Put Dave, Nicole, Brian, Lori at 10% each for next few months.

```{r}
n=9
round(difftime_func(n))
kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15) %>%
      row_spec(row = 0, color = "navy", background = "lightcyan")
```

## MBON (839115)

```{r}
n=12
x = format((pb$Cost[n]/pb$Budget[n])*100, digits = 2)
```

`r x`% spent

Hugh salary (28% Jan-June).

```{r}
n=12
round(difftime_func(n))
kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15) %>%
      row_spec(row = 0, color = "navy", background = "lightcyan")
```

## Cod Monitoring

```{r}
n=c(8,10,11,13,14)
x = format((pb$Cost[n]/pb$Budget[n])*100, digits = 2)
```

`r x`% spent.

REV Y1(836764), REV Y2 (836765), SRW Y1 (838999), REV Y3 (840787) & SRW Y2 (840788)

```{r}
n=c(8,10,11,13,14)
round(difftime_func(n)[1])
kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 12) %>%
      row_spec(row = 0, color = "navy", background = "lightcyan")
```

## MARACOOS

```{r}
n=c(15:21)
x = format((pb$Cost[n]/pb$Budget[n])*100, digits = 2)
```

`r x`% spent.   

Glider (831556), Mike (831557), Satellite (831558), HFR (831559), Data to Model (831936)

```{r}
n=c(15:21)
round(difftime_func(n)[1])
kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 12) %>%
      row_spec(row = 0, color = "navy", background = "lightcyan")
```
