---
title: "July 2026 Budget Review"
format: revealjs
editor: visual
---

```{r}
library(knitr)
library(tidyverse)
library(kableExtra)
library(dplyr)
library(gt)
library(lubridate)
library(readxl)

pb <- read_excel("~/Downloads/20260707_Projects Consolidated View By Task(3).xlsx", skip=3)
  #read_excel("~/Downloads/Balance Report 20250826 (1).xlsx", skip=3)
#pb = filter(pb, `Current Project Status Name` %in% "Active") 
pb$`Sponsor End Date` = as.POSIXct(pb$`Sponsor End Date`, format = "%m/%d/%Y")
pb = arrange(pb, `Sponsor End Date`)
pb = filter(pb, `Sponsor End Date` > "2026-01-01") %>%
  dplyr::select(-`Current Project Status Name`)
pb$Cost = pb$`Raw Cost` # names change in this file
            
difftime_func <- function(n){
    difftime(strptime(pb$`Sponsor End Date`[n], format = "%Y-%m-%d"), 
             + strptime("2026-07-09", format = "%Y-%m-%d"), 
             units="days")
  }
```

# Ended but active
## Cod Monitoring (VO underway)

```{r}
n = which(pb$`Project Number` %in% c(838999, 836764, 838765, 840787, 840788))
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```
`r x`% spent.

SRW Y1 (838999), REV Y1(836764), REV Y2 (836765), REV Y3 (840787) & SRW Y2 (840788). 

```{r}
n = which(pb$`Project Number` %in% c(838999, 836764, 838765, 840787, 840788))
round(difftime_func(n)[1])
kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 12) %>%
      row_spec(row = 0, color = "navy", background = "lightcyan")
```

## 2024 NJDEP (838607)

```{r}
n = which(pb$`Project Number` %in% 838607)
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```

`r x`% spent.

Buying new glider on insurance & user fee

```{r}
n = which(pb$`Project Number` %in% 838607)
round(difftime_func(n))
kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15) %>%
      row_spec(row = 0, color = "navy", background = "lightcyan")
```

## MBON (839115)

```{r}
n = which(pb$`Project Number` %in% 839115)
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```

`r x`% spent

Hugh Salary

```{r}
n = which(pb$`Project Number` %in% 839115)
round(difftime_func(n))
kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15) %>%
      row_spec(row = 0, color = "navy", background = "lightcyan")
```

# 3 Months

July - Sept 2026

## MARACOOS (Money coming)

```{r}
n = which(pb$`Project Number` %in% c(831556, 831557, 831558, 831559, 831561, 831934, 831936))
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```

`r x`% spent

```{r}
n = which(pb$`Project Number` %in% c(831556, 831557, 831558, 831559, 831561, 831934, 831936))
round(difftime_func(n))
new_table = pb[n,] %>% mutate(type = NA,
                              type = ifelse(`Project Number` %in% 831556, "Glider", type),
                              type = ifelse(`Project Number` %in% 831557, "Mike", type),
                              type = ifelse(`Project Number` %in% 831558, "Sat.", type),
                              type = ifelse(`Project Number` %in% 831559, "HFR", type),
                              type = ifelse(`Project Number` %in% 831561, "General", type),
                              type = ifelse(`Project Number` %in% 831934, "ROMS", type),
                              type = ifelse(`Project Number` %in% 831936, "Data2Model", type))
kable(new_table, format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 12) %>%
      row_spec(row = 0, color = "navy", background = "lightcyan")
```

## NYSERDA (834648)

```{r}
n = which(pb$`Project Number` %in% 834648)
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```

`r x`% spent.

```{r}
n = which(pb$`Project Number` %in% 834648)
round(difftime_func(n))
kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15) %>%
      row_spec(row = 0, color = "navy", background = "lightcyan")
```

## MOCEAN (837207)

```{r}
n = which(pb$`Project Number` %in% 837207)
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```

`r x`% spent.

Just had a meeting, the remaining funds went towards this. 

```{r}
n = which(pb$`Project Number` %in% 837207)
round(difftime_func(n))
kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15) %>%
      row_spec(row = 0, color = "navy", background = "lightcyan")
```

## Yale (840808)

```{r}
n = which(pb$`Project Number` %in% 840808)
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```

`r x`% spent.

```{r}
n = which(pb$`Project Number` %in% 840808)
round(difftime_func(n))
kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15) %>%
      row_spec(row = 0, color = "navy", background = "lightcyan")
```



## 6 months

Oct. - Dec. 2026

## BOEMRE NYB Sands (832319)

missing from the list, Julia & Laura

## SOCCOM (838815)

```{r}
n = which(pb$`Project Number` %in% 838815)
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```

`r x`% spent.

```{r}
n = which(pb$`Project Number` %in% 838815)
round(difftime_func(n))
kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15) %>%
      row_spec(row = 0, color = "navy", background = "lightcyan")
```

## Vineyard Mid-Atlantic (839357) 
(Final invoice sent a long time ago)

```{r}
n = which(pb$`Project Number` %in% 839357)
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```

`r x`% spent.

```{r}
n = which(pb$`Project Number` %in% 839357)
round(difftime_func(n))
kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15) %>%
      row_spec(row = 0, color = "navy", background = "lightcyan")
```

## BRI (839984)

```{r}
n = which(pb$`Project Number` %in% 839984)
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```

`r x`% spent.

```{r}
n = which(pb$`Project Number` %in% 839984)
round(difftime_func(n))
kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15) %>%
      row_spec(row = 0, color = "navy", background = "lightcyan")
```


