---
title: "RUCOOL June Budget Review"
format: revealjs
editor: visual
---

```{r}
library(knitr)
library(tidyverse)
library(kableExtra)
library(dplyr)
library(gt)
library(lubridate)
library(readxl)

pb <- read_excel("Downloads/Projects Consolidated View By Task(14).xlsx")
pb = filter(pb, `Project Status` %in% "Active")
pb$`Sponsor End Date` = as.POSIXct(pb$`Sponsor End Date`, format = "%m/%d/%Y")
```
# Under 3 months

# CINAR

```{r}
n=c(1:3,7)
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```
`r x`% spent

```{r}
n=c(1:3,7)
difftime(strptime(pb$`Sponsor End Date`[n], format = "%Y-%m-%d"), + strptime("2025-06-10", format = "%Y-%m-%d"),units="days")

kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15)
```
# Invenergy

```{r}
n=5
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```
`r x`% spent

Steve will fix this and bring it to zero

```{r}
n=5
difftime(strptime(pb$`Sponsor End Date`[n], format = "%Y-%m-%d"), + strptime("2025-06-10", format = "%Y-%m-%d"),units="days")

kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15)
```
# SNJ-DEP Glider 2024

```{r}
n=6
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```
`r x`% spent

Getting NCE

```{r}
n=6
difftime(strptime(pb$`Sponsor End Date`[n], format = "%Y-%m-%d"), + strptime("2025-06-10", format = "%Y-%m-%d"),units="days")

kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15)
```
# GOMO

```{r}
n=4
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```
`r x`% spent

Leah charging, some travel

```{r}
n=4
difftime(strptime(pb$`Sponsor End Date`[n], format = "%Y-%m-%d"), + strptime("2025-06-10", format = "%Y-%m-%d"),units="days")

kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15)
```
# MBON

```{r}
n=8
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```
`r x`% spent

Hugh charging only

```{r}
n=8
difftime(strptime(pb$`Sponsor End Date`[n], format = "%Y-%m-%d"), + strptime("2025-06-10", format = "%Y-%m-%d"),units="days")

kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15)
```
# MARACOOS

```{r}
n=c(9:13,15,16)
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```
`r x`% spent

Glider (Aug/Sept), Mike (Jan), Satellite (June - Steve will bring to zero), HFR (Nov or Feb), Modeling, Data to Model, DAC

```{r}
n=c(9:13,15,16)
difftime(strptime(pb$`Sponsor End Date`[n], format = "%Y-%m-%d"), + strptime("2025-06-10", format = "%Y-%m-%d"),units="days")

kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 10)
```
# UDel Hurricane Supplemental

```{r}
n=18
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```
`r x`% spent

Another chunk of money ($17k) from IRA for next hurricane deployment. Crowley (20%) and glider team will charge. 

```{r}
n=18
difftime(strptime(pb$`Sponsor End Date`[n], format = "%Y-%m-%d"), + strptime("2025-06-10", format = "%Y-%m-%d"),units="days")

kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15)
```
# UVI

```{r}
n=19
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```
`r x`% spent

```{r}
n=19
difftime(strptime(pb$`Sponsor End Date`[n], format = "%Y-%m-%d"), + strptime("2025-06-10", format = "%Y-%m-%d"),units="days")

kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15)
```
# Ramboll

```{r}
n=20
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```
`r x`% spent

Stopwork order. Daphne summer and then the remainder goes back. 

```{r}
n=20
difftime(strptime(pb$`Sponsor End Date`[n], format = "%Y-%m-%d"), + strptime("2025-06-10", format = "%Y-%m-%d"),units="days")

kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15)
```
# BPU Wind

```{r}
n=21
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```
`r x`% spent

Fernando 60%, Mike 10%, Julia 75%. Julia moved to 100% WOW March, then to BPU June. Need to figure out who else can charge here (Lori?). 

```{r}
n=21
difftime(strptime(pb$`Sponsor End Date`[n], format = "%Y-%m-%d"), + strptime("2025-06-10", format = "%Y-%m-%d"),units="days")

kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15)
```
# SOCCOM

```{r}
n=c(17,22)
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```
`r x`% spent

SOCCOM 2: Need to charge another month of Oscar, summer for Quentin, Mya, and Teemer. SOCCOM 3: Year 1 of 4

```{r}
n=c(17,22)
difftime(strptime(pb$`Sponsor End Date`[n], format = "%Y-%m-%d"), + strptime("2025-06-10", format = "%Y-%m-%d"),units="days")

kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15) 
```
# RIOS

```{r}
n=23
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```
`r x`% spent

```{r}
n=23
difftime(strptime(pb$`Sponsor End Date`[n], format = "%Y-%m-%d"), + strptime("2025-06-10", format = "%Y-%m-%d"),units="days")

kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15)
```
# Under 6 months

# SNJ-DEP Ecoglider Phase 1

```{r}
n=24
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```
`r x`% spent

100% Delphine, 65% Lori, 30% Jess, 30% Brian charging 

```{r}
n=24
difftime(strptime(pb$`Sponsor End Date`[n], format = "%Y-%m-%d"), + strptime("2025-06-10", format = "%Y-%m-%d"),units="days")

kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15)
```
# Cod - Sunrise

Jasco still needs to send final invoice (sent it for REV already). Steve is working on splitting the Jasco invoices between REV and SRW, most have already been moved. NCE for REV to next year. 

```{r}
n=25
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```
`r x`% spent

```{r}
n=25
difftime(strptime(pb$`Sponsor End Date`[n], format = "%Y-%m-%d"), + strptime("2025-06-10", format = "%Y-%m-%d"),units="days")

kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15)
```
# SNJ-DEP RMI Ocean Observing

```{r}
n=26
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```
`r x`% spent

```{r}
n=26
difftime(strptime(pb$`Sponsor End Date`[n], format = "%Y-%m-%d"), + strptime("2025-06-10", format = "%Y-%m-%d"),units="days")

kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15)
```
# Seaforestation

```{r}
n=27
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```
`r x`% spent

```{r}
n=27
difftime(strptime(pb$`Sponsor End Date`[n], format = "%Y-%m-%d"), + strptime("2025-06-10", format = "%Y-%m-%d"),units="days")

kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15)
```
