---
title: "RUCOOL April Budget Review"
format: revealjs
editor: visual
---

```{r}
library(readxl)
library(knitr)
library(tidyverse)
library(kableExtra)
library(dplyr)
library(gt)

pb <- read_excel("Downloads/COOL_03_2025_ProjectBalances.xlsx", sheet=2)
```

# Under 3 months

# Arete

```{r}
n=1
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```

`r x`% spent

Steve will spend out on salary

```{r}
n=1
difftime(strptime(pb$`Sponsor End Date`[n], format = "%Y-%m-%d"), + strptime("2025-04-01", format = "%Y-%m-%d"),units="days")
kable(pb[n,], format.args = list(big.mark = ","), booktabs = T) %>%
  kable_styling(font_size = 15)
```

# SNJ-DEP Clams

```{r}
n=2
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```

`r x`% spent

Got a 6 month NCE, the rest is for Grace to spend (ACTION ITEM LORI). Grace summer salary and funds for a technician to help with data workup from the CTD and pCO2 data.

```{r}
difftime(strptime(pb$`Sponsor End Date`[2], format = "%Y-%m-%d"), + strptime("2025-04-01", format = "%Y-%m-%d"),units="days")

kable(pb[2,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15)
```

# REV Y1

```{r}
n=3
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```

`r x`% spent

```{r}
n=3
difftime(strptime(pb$`Sponsor End Date`[n], format = "%Y-%m-%d"), + strptime("2025-04-01", format = "%Y-%m-%d"),units="days")

kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15)
```

# REV Y2

We do have a NCE

```{r}
n=4
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```

`r x`% spent

```{r}
n=4
difftime(strptime(pb$`Sponsor End Date`[n], format = "%Y-%m-%d"), + strptime("2025-04-01", format = "%Y-%m-%d"),units="days")

kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15)
```

# WHOI Turbine Hydrodynamics

```{r}
n=5
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```

`r x`% spent

More money is coming (\$176k)

```{r}
n=5
difftime(strptime(pb$`Sponsor End Date`[n], format = "%Y-%m-%d"), + strptime("2025-04-01", format = "%Y-%m-%d"),units="days")

kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15)
```

# SNJ-DEP Ecoglider Phase 1

```{r}
n=6
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```

`r x`% spent

Just got a NCE until Nov. 16. Need a salary forecast to see how much we can spend on equipment (ACTION ITEM MIKE, KAYCEE, LORI)

```{r}
n=6
difftime(strptime(pb$`Sponsor End Date`[n], format = "%Y-%m-%d"), + strptime("2025-04-01", format = "%Y-%m-%d"),units="days")

kable(pb[n,]) %>%
  kable_styling(font_size = 15)
```

# SNJ-DEP RMI Wind Turbine Coldpool

```{r}
n=7
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```

`r x`% spent

```{r}
n=7
difftime(strptime(pb$`Sponsor End Date`[n], format = "%Y-%m-%d"), + strptime("2025-04-01", format = "%Y-%m-%d"),units="days")

kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15)
```

# UDel Moffet Antarctic Fresh Water

```{r}
n=8
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```

`r x`% spent

Joe charging, Dave purchasing. Carlos might put in a NCE

```{r}
n=8
difftime(strptime(pb$`Sponsor End Date`[n], format = "%Y-%m-%d"), + strptime("2025-04-01", format = "%Y-%m-%d"),units="days")

kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15)
```

# Duke WoW

```{r}
n=9
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```

`r x`% spent

Will be getting another year. Isabella will be on this for two years.

```{r}
n=9
difftime(strptime(pb$`Sponsor End Date`[n], format = "%Y-%m-%d"), + strptime("2025-04-01", format = "%Y-%m-%d"),units="days")

kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15)
```

# SNJ-DEP RMI Ocean Observing

```{r}
n=10
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```

`r x`% spent

Will get a NCE

```{r}
n=10
difftime(strptime(pb$`Sponsor End Date`[n], format = "%Y-%m-%d"), + strptime("2025-04-01", format = "%Y-%m-%d"),units="days")

kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15)
```

## WHOI Ocean Acidification

```{r}
n=c(11:13)
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```

`r x`% spent

Medical person still needs to get moved off. Grace summer, Lori Salary

```{r}
n=c(11:13)
difftime(strptime(pb$`Sponsor End Date`[n], format = "%Y-%m-%d"), + strptime("2025-04-01", format = "%Y-%m-%d"),units="days")

kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15)
```

# WHOI GOMO TC

```{r}
n=14
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```

`r x`% spent

Leah charging, some travel, Joe G \$20K (salary commitment charges 3 months over)

```{r}
n=14
difftime(strptime(pb$`Sponsor End Date`[n], format = "%Y-%m-%d"), + strptime("2025-04-01", format = "%Y-%m-%d"),units="days")

kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15)
```

# Invenergy

```{r}
n=15
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```

`r x`% spent

Lori charging 25% (salary commitment charges 3 months over)

```{r}
n=15
difftime(strptime(pb$`Sponsor End Date`[n], format = "%Y-%m-%d"), + strptime("2025-04-01", format = "%Y-%m-%d"),units="days")

kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15)
```

# SNJ-BPU Wind Energy

```{r}
n=16
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```

`r x`% spent

Fernando 55%, Lori 35%, James 100%, Mike 5%. Travis and Scott summary salary in June

```{r}
n=16
difftime(strptime(pb$`Sponsor End Date`[n], format = "%Y-%m-%d"), + strptime("2025-04-01", format = "%Y-%m-%d"),units="days")

kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15)
```

# SNJ-DEP NJDEP Glider 2024

```{r}
n=17
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```

`r x`% spent

Requested a NCE for closed 2023 account. Need to request NCE for this one (ACTION ITEM LORI) also when do we expect 2025 contract?

```{r}
n=17
difftime(strptime(pb$`Sponsor End Date`[n], format = "%Y-%m-%d"), + strptime("2025-04-01", format = "%Y-%m-%d"),units="days")

kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15)
```

# WHOI CINAR Grace

```{r}
n=18
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```

`r x`% spent

Year 1 of 5 year cycle

```{r}
n=18
difftime(strptime(pb$`Sponsor End Date`[n], format = "%Y-%m-%d"), + strptime("2025-04-01", format = "%Y-%m-%d"),units="days")

kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15)
```

# UDel MBON

```{r}
n=19
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```

`r x`% spent

salary commitment charges 3 months over

```{r}
n=19
difftime(strptime(pb$`Sponsor End Date`[n], format = "%Y-%m-%d"), + strptime("2025-04-01", format = "%Y-%m-%d"),units="days")

kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15)
```

# Under 6 months

# MARACOOS

```{r}
n=c(20:27)
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```

`r x`% spent

Glider, Mike, Satellite, HFR, Modeling, ROMS, Data to Model, DAC

```{r}
n=c(20:27)
difftime(strptime(pb$`Sponsor End Date`[n], format = "%Y-%m-%d"), + strptime("2025-04-01", format = "%Y-%m-%d"),units="days")

kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 10)

```

# NYSERDA

```{r}
n=28
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```

`r x`% spent

Working on NCE until Aug. 2026. Buying DMON (ordered). Sam Alaimo. ACTION ITEM TRAVIS AND LAURA

```{r}
n=28
difftime(strptime(pb$`Sponsor End Date`[n], format = "%Y-%m-%d"), + strptime("2025-04-01", format = "%Y-%m-%d"),units="days")

kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15)
```

# NASA

```{r}
n=30
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```

`r x`% spent

Subaward commitments. Grad students (\$19k) and 2 months summer salary

```{r}
n=30
difftime(strptime(pb$`Sponsor End Date`[n], format = "%Y-%m-%d"), + strptime("2025-04-01", format = "%Y-%m-%d"),units="days")

kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15)
```

# UDel Hurricane Supplemental

```{r}
n=31
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```

`r x`% spent

Another chunk of money (\$17k) from IRA for next hurricane deployment.

```{r}
n=31
difftime(strptime(pb$`Sponsor End Date`[n], format = "%Y-%m-%d"), + strptime("2025-04-01", format = "%Y-%m-%d"),units="days")

kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15)
```

# UVI

```{r}
n=32
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```

`r x`% spent

```{r}
n=32
difftime(strptime(pb$`Sponsor End Date`[n], format = "%Y-%m-%d"), + strptime("2025-04-01", format = "%Y-%m-%d"),units="days")

kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15)
```

# Ramboll

```{r}
n=33
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```

`r x`% spent

Unofficial stop work order received

```{r}
n=33
difftime(strptime(pb$`Sponsor End Date`[n], format = "%Y-%m-%d"), + strptime("2025-04-01", format = "%Y-%m-%d"),units="days")

kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15)
```

# U of Cal. San Diego SOCCOM 3

```{r}
n=34
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```

`r x`% spent

Year 1 of 3. Salary for grad student

```{r}
n=34
difftime(strptime(pb$`Sponsor End Date`[n], format = "%Y-%m-%d"), + strptime("2025-04-01", format = "%Y-%m-%d"),units="days")

kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15) 
```
