---
title: "April 2026 Budget Review"
format: revealjs
editor: visual
---

```{r}
library(knitr)
library(tidyverse)
library(kableExtra)
library(dplyr)
library(gt)
library(lubridate)
library(readxl)

pb <- read_excel("~/Downloads/20260331 Balances Projects Consolidated View.xlsx", skip=3)
  #read_excel("~/Downloads/Balance Report 20250826 (1).xlsx", skip=3)
#pb = filter(pb, `Current Project Status Name` %in% "Active") 
pb$`Sponsor End Date` = as.POSIXct(pb$`Sponsor End Date`, format = "%m/%d/%Y")
pb = arrange(pb, `Sponsor End Date`)
pb = filter(pb, `Sponsor End Date` > "2026-01-01") %>%
  dplyr::select(-`Current Project Manager`,-`Project Description`,-`Current Project Status Name`)
pb$Cost = pb$`Raw Cost` # names change in this file
            
difftime_func <- function(n){
    difftime(strptime(pb$`Sponsor End Date`[n], format = "%Y-%m-%d"), 
             + strptime("2026-04-07", format = "%Y-%m-%d"), 
             units="days")
  }
```

# 3 Months

April - June 2026

## MOCEAN (837207)

```{r}
n=2
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```

`r x`% spent.

Remaining goes to Sarah and Daphne for white paper

```{r}
n=2
round(difftime_func(n))
kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15) %>%
      row_spec(row = 0, color = "navy", background = "lightcyan")
```


## WHOI wind wakes Nantucket Shoals

```{r}
n=4
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```

`r x`% spent

```{r}
n=4
round(difftime_func(n))
kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15) %>%
      row_spec(row = 0, color = "navy", background = "lightcyan")
```

## ASOW Lidar at RUMFS (837206)

```{r}
n=5
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```

`r x`% spent.


```{r}
n=5
difftime_func(n)
kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15) %>%
      row_spec(row = 0, color = "navy", background = "lightcyan")
```


## UDel CAREER

```{r}
n=5
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```

`r x`% spent

```{r}
n=5
difftime_func(n)
kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15) %>%
      row_spec(row = 0, color = "navy", background = "lightcyan")
```

## 2024 NJDEP

```{r}
n=7
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```

`r x`% spent


```{r}
n=7
round(difftime_func(n))
kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15) %>%
      row_spec(row = 0, color = "navy", background = "lightcyan")
```

## MBON

```{r}
n=10
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```

`r x`% spent

Hugh Salary

```{r}
n=10
round(difftime_func(n))
kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15) %>%
      row_spec(row = 0, color = "navy", background = "lightcyan")
```

## Cod Monitoring at 

```{r}
n=c(6,8,9,11,12)
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```

`r x`% spent.

SRW Y1 (838999), REV Y1(836764), REV Y2 (836765), REV Y3 (840787) & SRW Y2 (840788). ~$250k remaining 

```{r}
n=c(6,8,9,11,12)
round(difftime_func(n)[1])
kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 12) %>%
      row_spec(row = 0, color = "navy", background = "lightcyan")
```


## 6 months
Oct 2026

## MARACOOS
```{r}
n=13:19
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```

`r x`% spent

```{r}
n=13:19
round(difftime_func(n))
kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 12) %>%
      row_spec(row = 0, color = "navy", background = "lightcyan")
```

## BOEMRE NYB Sands (832319)

```{r}
n=22
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```

`r x`% spent.

Need to figure out spending for Mike/Tim

```{r}
n=22
round(difftime_func(n))
kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15) %>%
      row_spec(row = 0, color = "navy", background = "lightcyan")
```


## SOCCOM (838815)

```{r}
n=23
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```

`r x`% spent.

```{r}
n=23
round(difftime_func(n))
kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15) %>%
      row_spec(row = 0, color = "navy", background = "lightcyan")
```

## Summer Salary

