---
title: "October Budget Review"
format: revealjs
editor: visual
---

```{r}
library(knitr)
library(tidyverse)
library(kableExtra)
library(dplyr)
library(gt)
library(lubridate)
library(readxl)

pb <- read_excel("~/Downloads/Balance 20251020 Projects Consolidated View By Task(22) (1).xlsx", skip=3)
  #read_excel("~/Downloads/Balance Report 20250826 (1).xlsx", skip=3)
pb = filter(pb, `Current Project Status Name` %in% "Active") 
pb$`Sponsor End Date` = as.POSIXct(pb$`Project End Date`, format = "%m/%d/%Y")
pb = arrange(pb, `Sponsor End Date`)

difftime_func <- function(n){
    difftime(strptime(pb$`Sponsor End Date`[n], format = "%Y-%m-%d"), 
             + strptime("2025-09-16", format = "%Y-%m-%d"), 
             units="days")
  }
```

# No 3 month end dates

# 6 Months

April 2026

## RMI Ecoglider Phase 1 (832349)

```{r}
n=1
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```

`r x`% spent

100% Delphine, 95% Lori, 50% Jess, 70% Brian charging, 35% Dave, 10% Waite. Jake salary, fall salary and tuition for Sam, Ashley, and Izzy tuition, Lauren summer.

```{r}
n=1
difftime_func(n)
kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15) %>%
      row_spec(row = 0, color = "navy", background = "lightcyan")
```

## RMI Ocean Observing (834812)

```{r}
n=2
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```

`r x`% spent

All for subcontracts (\~\$53k)

```{r}
n=2
difftime_func(n)
kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15) %>%
      row_spec(row = 0, color = "navy", background = "lightcyan")
```

## Ørsted Sunrise Cod (838999)

```{r}
n=c(3)
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```

`r x`% spent.

Working on extension to June 2026

```{r}
n=c(3)
difftime_func(n)
kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15) %>%
      row_spec(row = 0, color = "navy", background = "lightcyan")
```


## WOW (833804)

```{r}
n=4
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```

`r x`% spent

Unknown if we will be getting another year

```{r}
n=4
difftime_func(n)
kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15) %>%
      row_spec(row = 0, color = "navy", background = "lightcyan")
```

## Seaforestation (836582)

```{r}
n=5
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```

`r x`% spent

Travel, Jess (40-30%), Dave (15%), Lori (5%). 

```{r}
n=5
difftime_func(n)
kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15) %>%
      row_spec(row = 0, color = "navy", background = "lightcyan")
```

## Ørsted OCW01 Data Archival (839573)

```{r}
n=6
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```

`r x`% spent

Salary for Kaycee (35-70%), Motz, Tim (40%), Smith (40%), Delphine (11 d), Joey (50%)

```{r}
n=6
difftime_func(n)
kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15) %>%
      row_spec(row = 0, color = "navy", background = "lightcyan")
```

## WAP UConn (837205)

```{r}
n=7
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```

`r x`% spent

Mostly students (Teemer, Myam Quintin) and people we send to Antarctica. Account was set up late

```{r}
n=7
difftime_func(n)
kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15) %>%
      row_spec(row = 0, color = "navy", background = "lightcyan")
```

<!-- ## MOCEAN (837207) -->

<!-- ```{r} -->
<!-- n=8 -->
<!-- x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2) -->
<!-- ``` -->

<!-- `r x`% spent.\ -->
<!-- Money for Sarah and Daphne -->

<!-- ```{r} -->
<!-- n=8 -->
<!-- difftime_func(n) -->
<!-- kable(pb[n,], format.args = list(big.mark = ",")) %>% -->
<!--   kable_styling(font_size = 15) %>% -->
<!--       row_spec(row = 0, color = "navy", background = "lightcyan") -->
<!-- ``` -->

<!-- ## BOEM NYB Sands (832319) -->

<!-- ```{r} -->
<!-- n=19 -->
<!-- x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2) -->
<!-- ``` -->

<!-- `r x`% spent -->

<!-- Tim (40%) and Smith (40%) helping with ERDDAP -->

<!-- ```{r} -->
<!-- n=19 -->
<!-- difftime_func(n) -->
<!-- kable(pb[n,], format.args = list(big.mark = ",")) %>% -->
<!--   kable_styling(font_size = 15) %>% -->
<!--       row_spec(row = 0, color = "navy", background = "lightcyan") -->
<!-- ``` -->

<!-- ## ASOW RUMFS Lidar (837206) -->

<!-- ```{r} -->
<!-- n=10 -->
<!-- x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2) -->
<!-- ``` -->

<!-- `r x`% spent -->

<!-- Roland -->

<!-- ```{r} -->
<!-- n=10 -->
<!-- difftime_func(n) -->
<!-- kable(pb[n,], format.args = list(big.mark = ",")) %>% -->
<!--   kable_styling(font_size = 15)  %>% -->
<!--       row_spec(row = 0, color = "navy", background = "lightcyan") -->
<!-- ``` -->

<!-- # The End -->
