---
title: "RUCOOL May Budget Review"
format: revealjs
editor: visual
---

```{r}
library(readr)
library(knitr)
library(tidyverse)
library(kableExtra)
library(dplyr)
library(gt)
library(lubridate)

pb <- read_csv("Downloads/202508 Projects Consolidated View By Task end date(Sheet1).csv")
pb1 = filter(pb, `Project Status` %in% "Active")
pb = dplyr::select(pb1, `Project Number`,`Project Description`,`Sponsor End Date`,`Principal Investigator`,`Budget`,`Total Actual Cost`,`Commitments`,`Available Balance Without Commitments`)

pb1 = dplyr::select(pb1, `Project Number`,`Project Description`,`Sponsor End Date`,`Principal Investigator`,`Budget`,`Commitments`,`Actual Balance Without Commitments`)

pb$`Sponsor End Date` = as.POSIXct(pb$`Sponsor End Date`, format = "%m/%d/%Y")
```

# Under 3 months

# SNJ-DEP RMI Wind Turbine Coldpool

```{r}
n=3
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```
`r x`% spent

```{r}
n=3
difftime(strptime(pb$`Sponsor End Date`[n], format = "%Y-%m-%d"), + strptime("2025-05-13", format = "%Y-%m-%d"),units="days")

kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15)
```

# UDel Moffet Antarctic Fresh Water

```{r}
n=4
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```
`r x`% spent

Joe charging (50%). NCE coming

```{r}
n=4
difftime(strptime(pb$`Sponsor End Date`[n], format = "%Y-%m-%d"), + strptime("2025-04-01", format = "%Y-%m-%d"),units="days")

kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15)
```

# CINAR

```{r}
n=c(5,7,8,11)
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```
`r x`% spent

Medical person still needs to get moved off. Grace summer, Lori Salary

```{r}
n=c(5,7,8,11)
difftime(strptime(pb$`Sponsor End Date`[n], format = "%Y-%m-%d"), + strptime("2025-04-01", format = "%Y-%m-%d"),units="days")

kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15)
```

# Duke WOW

```{r}
n=6
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```
`r x`% spent

Will be getting another year? Isabella will be on this for two years.

```{r}
n=6
difftime(strptime(pb$`Sponsor End Date`[n], format = "%Y-%m-%d"), + strptime("2025-04-01", format = "%Y-%m-%d"),units="days")

kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15)
```
# GOMO

```{r}
n=9
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```
`r x`% spent

Leah charging, some travel, Joe G $20K (salary commitment charges 3 months over)

```{r}
n=9
difftime(strptime(pb$`Sponsor End Date`[n], format = "%Y-%m-%d"), + strptime("2025-04-01", format = "%Y-%m-%d"),units="days")

kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15)
```
# Invenergy

```{r}
n=10
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```
`r x`% spent

Lori charging 25% and will spend out in June

```{r}
n=10
difftime(strptime(pb$`Sponsor End Date`[n], format = "%Y-%m-%d"), + strptime("2025-04-01", format = "%Y-%m-%d"),units="days")

kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15)
```
# MBON

```{r}
n=12
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```
`r x`% spent

Hugh charging only

```{r}
n=12
difftime(strptime(pb$`Sponsor End Date`[n], format = "%Y-%m-%d"), + strptime("2025-04-01", format = "%Y-%m-%d"),units="days")

kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15)
```
# MARACOOS

```{r}
n=c(13:16)
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```
`r x`% spent

Glider: will run out Aug/Sept. John charging what glider team doesn't use. 

Mike: Will run out in Jan. 

Satellite: Will run out in early June

HFR: will run out Nov 15 unless DARPA comes for Hugh and Tim (then Feb 1 end)

```{r}
n=c(13:16)
difftime(strptime(pb$`Sponsor End Date`[n], format = "%Y-%m-%d"), + strptime("2025-04-01", format = "%Y-%m-%d"),units="days")

kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 10)
```

# Data to Model

```{r}
n=19
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```
`r x`% spent

```{r}
n=19
difftime(strptime(pb$`Sponsor End Date`[n], format = "%Y-%m-%d"), + strptime("2025-04-01", format = "%Y-%m-%d"),units="days")

kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15)
```
# GEO

```{r}
n=20
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```
`r x`% spent

```{r}
n=20
difftime(strptime(pb$`Sponsor End Date`[n], format = "%Y-%m-%d"), + strptime("2025-04-01", format = "%Y-%m-%d"),units="days")

kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15)
```
# Under 6 months

# SOCCOM 

```{r}
n=c(22,27)
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```
`r x`% spent

SOCCUM 2: Need to charge another month of Oscar, summer for Quentin, Mya, and Teemer.
SOCCUM 3: Year 1 of 4

```{r}
n=c(22,27)
difftime(strptime(pb$`Sponsor End Date`[n], format = "%Y-%m-%d"), + strptime("2025-04-01", format = "%Y-%m-%d"),units="days")

kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15) 
```
# UDel Hurricane Supplemental

```{r}
n=23
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```
`r x`% spent

Another chunk of money ($17k) from IRA for next hurricane deployment.

```{r}
n=23
difftime(strptime(pb$`Sponsor End Date`[n], format = "%Y-%m-%d"), + strptime("2025-04-01", format = "%Y-%m-%d"),units="days")

kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15)
```
# UVI

```{r}
n=24
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```
`r x`% spent

```{r}
n=24
difftime(strptime(pb$`Sponsor End Date`[n], format = "%Y-%m-%d"), + strptime("2025-04-01", format = "%Y-%m-%d"),units="days")

kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15)
```
# BPU

```{r}
n=26
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```
`r x`% spent

Fernando 60%, Mike 10%, Julia 75%

```{r}
n=26
difftime(strptime(pb$`Sponsor End Date`[n], format = "%Y-%m-%d"), + strptime("2025-04-01", format = "%Y-%m-%d"),units="days")

kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15)
```
# RMI Daphne

```{r}
n=28
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```
`r x`% spent

Grace summer salary and funds for a technician to help with data workup from the CTD and pCO2 data.

```{r}
n=28
difftime(strptime(pb$`Sponsor End Date`[n], format = "%Y-%m-%d"), + strptime("2025-04-01", format = "%Y-%m-%d"),units="days")

kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15)
```
# RIOS

```{r}
n=29
x = format((pb$`Total Actual Cost`[n]/pb$Budget[n])*100, digits = 2)
```
`r x`% spent

```{r}
n=29
difftime(strptime(pb$`Sponsor End Date`[n], format = "%Y-%m-%d"), + strptime("2025-04-01", format = "%Y-%m-%d"),units="days")

kable(pb[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15)
```

# Gifts Review

# Gifts

```{r}
n=c(46:50)
kable(pb1[n,], format.args = list(big.mark = ",")) %>%
  kable_styling(font_size = 15)
```

